Misexpression of germline programs with loss of the X-linked intellectual disability factor KDM5C

### 2024-04-18 submission/manuscript.Rmd
add ovary/germline gene section

Interestingly, we also observed significant enrichment of ovary genes within the male _Kdm5c_-KO brain (Amygdala p = `r signif(gettissval("Amygdala_pvalues", "Ovary"), 3)`; Hippocampus p = `r signif(gettissval("Hippocampus_pvalues", "Ovary"), 3)`, Fisher's Exact). Although there are relatively few ovary-enriched DEGs compared to testis-DEGs (Amygdala: `r gettissval("Amygdala_DEGnumb", "Testis")` testis DEGs, `r gettissval("Amygdala_DEGnumb", "Ovary")` ovary DEGs; Hippocampus: `r gettissval("Hippocampus_DEGnumb", "Testis")` testis DEGs, `r gettissval("Hippocampus_DEGnumb", "Ovary")` ovary DEGs), they also had known germline-specific functions. For example, _Zygotic arrest 1 (Zar1)_ was recently shown to regulate oocyte translation by sequestering mRNAs[@chengMammalianOocytesStore2022] (Figure 1D).

>>>>

Interestingly, we also observed significant enrichment of ovary genes within the male _Kdm5c_-KO brain (Amygdala p = `r signif(gettissval("Amygdala_pvalues", "Ovary"), 3)`; Hippocampus p = `r signif(gettissval("Hippocampus_pvalues", "Ovary"), 3)`, Fisher's Exact). Although there are relatively few ovary-enriched DEGs compared to testis-DEGs (Amygdala: `r gettissval("Amygdala_DEGnumb", "Testis")` testis DEGs, `r gettissval("Amygdala_DEGnumb", "Ovary")` ovary DEGs; Hippocampus: `r gettissval("Hippocampus_DEGnumb", "Testis")` testis DEGs, `r gettissval("Hippocampus_DEGnumb", "Ovary")` ovary DEGs), they also have known germline-specific functions. For example, _Zygotic arrest 1 (Zar1)_ was recently shown to regulate oocyte translation by sequestering mRNAs[@chengMammalianOocytesStore2022] (Figure 1D).
